SparseIDS: Learning Packet Sampling with Reinforcement Learning

### 2020-02-07 paper_rl/paper.tex
Change caption of training figure
reposition tables + note about time steps

\begin{figure}[h]
\centering
%  \includegraphics[width=\columnwidth]{{"img/events.out.tfevents.1579352256.gpu"}.pdf}
  \includegraphics[width=\columnwidth]{{"img/events.out.tfevents.1580988920.gpu"}.pdf}
  \caption{Training with a tradeoff of 0.1 with continuous actions. Training accuracy increases sharply in the beginning while becoming slower later on. Sparsity increases sharply in the beginning and then more slowly. As the classifier gets better, the \gls{rl} starts skipping more packets.}
  \label{fig:training}
\end{figure}

@@

\begin{table}
\caption{Comparing classification metrics per flow with different tradeoffs. The higher the tradeoff, the higher the sparsity but also the lower the accuracy.} \label{tab:results_tradeoff}
\centering
\begin{tabular}{>{\rowmac}l >{\rowmac}r>{\rowmac}r>{\rowmac}r>{\rowmac}r<{\clearrow}} \toprule
Tradeoff & 0.0 & 0.1 & 0.5 & 1.0 \\	\midrule
\setrow{\bfseries}Sparsity & 0\% & 76.3\% & 76.5\% & 76.8\% \\ \midrule
\setrow{\bfseries}Accuracy & 99.5\% & 99.4\% & 99.3\% & 99.0\% \\
Precision & 99.4\% & 98.5\% & 98.7\% & 97.9\% \\
Recall & 98.5\% & 99.0\% & 98.6\% & 98.1\% \\
F1 & 99.0\% & 98.7\% & 98.6\% & 98.0\% \\
Youden & 98.4\% & 98.5\% & 98.2\% & 97.4\% \\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Comparing classification metrics per flow between \gls{rl}-based sampling with continuous actions (tradeoff $0.1$) and alternative strategies.} \label{tab:results_others}
\centering
\begin{tabular}{>{\rowmac}l >{\rowmac}r>{\rowmac}r>{\rowmac}r>{\rowmac}r>{\rowmac}r<{\clearrow}} \toprule
& \gls{rl} & random & every $i$th & relative first \emph{m} & first \emph{m} \\	\midrule
\setrow{\bfseries}Sparsity & 76.3\% & 76.3\% & 76.3\% & 76.3\% & 76.3\% \\ \midrule
\setrow{\bfseries}Accuracy & 99.4\% & 96.9\% & 97.8\% & 97.3\% & 98.3\% \\
Precision & 98.5\% & 92.4\% & 95.8\% & 93.8\% & 95.6\% \\
Recall & 99.0\% & 95.6\% & 95.4\% & 95.5\% & 97.9\% \\
F1 & 99.7\% & 94.0\% & 95.6\% & 94.7\% & 96.7\% \\
Youden & 98.5\% & 93.0\% & 93.9\% & 93.4\% & 96.4\% \\
\bottomrule
\end{tabular}
\end{table}

@@

>>>>

\begin{figure}[h]
\centering
%  \includegraphics[width=\columnwidth]{{"img/events.out.tfevents.1579352256.gpu"}.pdf}
  \includegraphics[width=\columnwidth]{{"img/events.out.tfevents.1580988920.gpu"}.pdf}
  \caption{Training with a tradeoff of 0.1 with continuous actions. Training accuracy increases sharply in the beginning while increasing more slowly later on. The behavior for sparsity is similar. As the classifier gets better, the \gls{rl} starts skipping more packets.}
  \label{fig:training}
\end{figure}

@@

\begin{table*}
\parbox{.45\linewidth}{
\caption{Comparing classification metrics per flow with different tradeoffs. The higher the tradeoff, the higher the sparsity but also the lower the accuracy.} \label{tab:results_tradeoff}
\centering
\begin{tabular*}{\columnwidth}{>{\rowmac}l @{\extracolsep{\fill}} >{\rowmac}c>{\rowmac}c>{\rowmac}c>{\rowmac}c<{\clearrow}} \toprule
Tradeoff & 0.0 & 0.1 & 0.5 & 1.0 \\	\midrule
\setrow{\bfseries}Sparsity & 0\% & 76.3\% & 76.5\% & 76.8\% \\ \midrule
\setrow{\bfseries}Accuracy & 99.5\% & 99.4\% & 99.3\% & 99.0\% \\
Precision & 99.4\% & 98.5\% & 98.7\% & 97.9\% \\
Recall & 98.5\% & 99.0\% & 98.6\% & 98.1\% \\
F1 & 99.0\% & 98.7\% & 98.6\% & 98.0\% \\
Youden & 98.4\% & 98.5\% & 98.2\% & 97.4\% \\
\bottomrule
\end{tabular*}
}
\hspace{0.8cm}
\parbox{.45\linewidth}{
\caption{Comparing classification metrics per flow between \gls{rl}-based sampling with continuous actions (tradeoff $0.1$) and alternative strategies.} \label{tab:results_others}
\centering
\begin{tabular*}{\columnwidth}{>{\rowmac}l @{\extracolsep{\fill}} >{\rowmac}c>{\rowmac}c>{\rowmac}c>{\rowmac}c>{\rowmac}c<{\clearrow}} \toprule
& \gls{rl} & random & every $i$th & relative first \emph{m} & first \emph{m} \\	\midrule
\setrow{\bfseries}Sparsity & 76.3\% & 76.3\% & 76.3\% & 76.3\% & 76.3\% \\ \midrule
\setrow{\bfseries}Accuracy & 99.4\% & 96.9\% & 97.8\% & 97.3\% & 98.3\% \\
Precision & 98.5\% & 92.4\% & 95.8\% & 93.8\% & 95.6\% \\
Recall & 99.0\% & 95.6\% & 95.4\% & 95.5\% & 97.9\% \\
F1 & 99.7\% & 94.0\% & 95.6\% & 94.7\% & 96.7\% \\
Youden & 98.5\% & 93.0\% & 93.9\% & 93.4\% & 96.4\% \\
\bottomrule
\end{tabular*}
}
\end{table*}

@@

%\begin{table}
%\caption{Comparing classification metrics per flow between \gls{rl}-based sampling with continuous actions (tradeoff $0.1$) and alternative strategies.} \label{tab:results_others}
%\centering
%\begin{tabular}{>{\rowmac}l >{\rowmac}c>{\rowmac}c>{\rowmac}c>{\rowmac}c>{\rowmac}c<{\clearrow}} \toprule
%& \gls{rl} & random & every $i$th & relative first \emph{m} & first \emph{m} \\	\midrule
%\setrow{\bfseries}Sparsity & 76.3\% & 76.3\% & 76.3\% & 76.3\% & 76.3\% \\ \midrule
%\setrow{\bfseries}Accuracy & 99.4\% & 96.9\% & 97.8\% & 97.3\% & 98.3\% \\
%Precision & 98.5\% & 92.4\% & 95.8\% & 93.8\% & 95.6\% \\
%Recall & 99.0\% & 95.6\% & 95.4\% & 95.5\% & 97.9\% \\
%F1 & 99.7\% & 94.0\% & 95.6\% & 94.7\% & 96.7\% \\
%Youden & 98.5\% & 93.0\% & 93.9\% & 93.4\% & 96.4\% \\
%\bottomrule
%\end{tabular}
%\end{table}

@@

% Fares: if figures are not changed add "The time steps represent the index of the sampled packets." to the caption
